SpecHunter: Interactively Inferring Taint Specifications Using Bayes Net

### 2021-04-04 My-Papers/SpecHunter/paper.tex
add similarity edges detail

% 무슨 environment를 써야 하나...? 일단 적어보쟈

\begin{align*}
  A\in \mathbb{D} = \mathbb{C}\rightarrow\mathcal{P}(State)\\
  s\in State = Procname\times Var\times Loc\times Alias\\
  p\in Procname \subseteq Var\\
  a\in Alias \subseteq \mathcal{P}(Var)
\end{align*}

@@

\begin{itemize}

\item \texttt{\{(f, x, 14, \{x, y\})\}}
\item \texttt{\{(g, y, 18, \{y, u1\})\}}
\item \texttt{\{(m2, u1, 5, \{u1\})\}}
\item \texttt{\{(m2, u1, 6, \{u1\})\}}
\item \texttt{\{(g, z, 6, \{z, u1, w\})\}}
\item \texttt{\{(g, w, 23, \{w, u2\})\}}
\item \texttt{\{(m3, u2, 9, \{u2, println_1\})\}}

\end{itemize}

where \texttt{println_1} is a Mangled parameter variable of \texttt{println}.
Now, connecting the tuples with the aliases, we get two chains: \texttt{x -> y
  -> u1} and \texttt{u1 -> z -> w -> u2 -> println_1}. Since \texttt{u1} is
redefined in \texttt{m2}, we glue the two together to get the originally desired
information: \texttt{x -> y -> u1 -> z -> w -> u2 -> println_1}. This translates
into data-flow edges: \texttt{(f, g)}, \texttt{(f, h)}, and \texttt{(m3, println)}.

% 아 이거 실제로 돌려봐서 확인해야 할 거 같은뎅.. 실제로 이렇게 나오나...?

@@

Last but not least, there are similarity-edges. The idea is to take any two
methods and score its pairwise similarity, and leave only the pairs with score
above a predefined threshold.
% TODO syntactic, semantic feature 표 넣기

>>>>

\begin{align*}
  A &\in \mathbb{D} &= \mathbb{C}\rightarrow\mathcal{P}(State)\\
  s &\in State &= Procname\times Var\times Loc\times Alias\\
  p &\in Procname &\subseteq Var\\
  a &\in Alias &\subseteq \mathcal{P}(Var)
\end{align*}

@@

\begin{itemize}
\item \texttt{\{(f, x, 14, \{x, y\})\}}
\item \texttt{\{(g, y, 18, \{y, u1\})\}}
\item \texttt{\{(m2, u1, 5, \{u1\})\}}
\item \texttt{\{(m2, u1, 6, \{u1\})\}}
\item \texttt{\{(g, z, 6, \{z, u1, w\})\}}
\item \texttt{\{(g, w, 23, \{w, u2\})\}}
\item \texttt{\{(m3, u2, 9, \{u2, println\_1\})\}}
\end{itemize}

>
where \texttt{println\_1} is a Mangled parameter variable of \texttt{println}.
Now, connecting the tuples with the aliases, we get two chains:
\texttt{x -> y -> u1} and \texttt{u1 -> z -> w -> u2 -> println\_1}. Since \texttt{u1} is
redefined in \texttt{m2}, we glue the two together to get the originally desired
information: \texttt{x -> y -> u1 -> z -> w -> u2 -> println\_1}. This translates
into data-flow edges: \texttt{(f, g)}, \texttt{(f, h)}, and \texttt{(m3, println)}.

% TODO 아 이거 실제로 돌려봐서 확인해야 할 거 같은뎅.. 실제로 이렇게 나오나...?

@@

Last but not least, there are similarity-edges. The idea is to take any two
methods and score its pairwise similarity, and leave only the pairs with score
above a predefined threshold. We measure them against two large groups of
criteria: the ``syntactic features'' and ``semantic features''. For the
syntactic features, we borrrowed largely from \textbf{Swan}'s features that
check how names of methods or their return types are composed. The below
figure % TODO: Figure 번호 달기...
shows all the features we used.

% TODO 표 삐져나간다..!!!!
\begin{center}
  \begin{tabular} { |c|c|c| }
    \hline
    Syntactic & Semantic\\
    \hline
    \hline
    Both has parameters? & Both has at least one same callee?\\
    Both has return type? & Both are making calls but not passing data?\\
    Both contains same word in method name? & Both are being called but not being passed data?\\
    Both contains same word in class name? & Both are making data flow calls?\\
    Both has return type contained in parameter type? & Both are being passed data and passing data simultaneously?\\
    Both has same return type? & Both are being passed data which gets dead in them?\\
    Both has return type contained in method name? & Both has variable redefinitions?\\
    \hline
  \end{tabular}
\end{center}
